
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Tools and Problems}
\label{chap:Methodology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tools to be used}
This educational system will be a web application for accessibility. A Python back-end using the Django framework will enable the use of Qiskit for running quantum algorithms, while the React TypeScript front-end will facilitate building interactive components. I am considering using Angular as a learning opportunity, but I am mindful of the need to manage my time effectively due to the steep quantum computing learning curve. I will determine if that is possible in the coming weeks as I experiment with the project setup.



\section{Potential problems}

Firstly, I have set some bold project specifications for someone who has just jumped into quantum computing armed with enthusiasm and not much else. I am particularly aware of the challenges in developing a Qiskit lab environment to execute algorithms and circuits, as I currently lack the knowledge needed to integrate Qiskit into the platform effectively. Only further research and trials will remedy this.\\

\noindent {There is also the issue of simulating quantum algorithms using classical computing. As I understand, as long as I do not work with too many qubits, classical simulation should be manageable. I require further research to determine the feasibility of this.}\\

\noindent {Another potential problem is presenting complex quantum concepts in a simple, accessible manner. I aim to dive slightly deeper than existing online resources, but explaining abstract ideas without overwhelming learners or losing accuracy will require careful thought. I expect that observing other learning resources will help structure the material effectively. } \\

\noindent {Finally, this project will require exceptional time management. Balancing learning quantum computing, producing learning material, developing the web application and writing the dissertation will be a challenge. Developing the front-end will surely be a feat in itself. I may need to redefine some project requirements or scope, staying flexible in addressing challenges while ensuring the project remains organized and on track. }\\
